Colorism and Cosmetics: Investigating Limited Shade Ranges in the Beauty Industry in Japan and India\thanks{Code and data supporting this analysis is available at:}

### 2023-04-21 outputs/paper/paper.tex
Update version with citations

---
title: "Colorism and Cosmetics: Investigating Limited Shade Ranges in the Beauty Industry in Japan and India"
format: pdf
author: "Laura Lee-Chu"
abstract: "This research paper explores the issue of colorism in the context of the beauty industry in Japan and India. Drawing on data from an article published by The Pudding, the paper focuses on the association between the lightness and saturation of foundation shades provided by leading makeup brands in India and Japan. The findings reveal a preference for lighter shades in international brands, whereas domestic brands offer a broader spectrum of shades with warmer undertones. The study uncovers a negative correlation between the saturation and lightness of foundation shades, with Japanese foundation shades being paler and having an ashier tone, and Indian foundation shades being substantially lighter than the natural skin tone. The scarcity of foundation shades for individuals with darker skin tones can lead to their marginalization and exclusion, perpetuating the issue of colorism in the beauty industry."
date: today
date-format: long
editor: visual
toc: TRUE
number-sections: TRUE
bibliography: references.bib
thanks: "Code and data supporting this analysis is available at: "
---

```{r}
#| messages: false
#| echo: false
#| warning: false
#| output: false

#### Preamble ####
# Title:
# Author: Laura Lee-Chu
# Email: 
# Date: 16 March 2023

#### Work space set-up ####
# Define required libraries

library(tidyverse)
library(dplyr)
library(tidyr)
library(knitr)
library(janitor)
library(scales)
library(ggplot2)
library(kableExtra)
library(here)
library(readr)
library(kableExtra)
library(broom)

# Fetching the shade range data 
cleanshades <- readr::read_csv(here::here("inputs/data/clean/cleanshades.csv"), show_col_types = FALSE)

lightnessrange <- readr::read_csv(here::here("inputs/data/clean/lightnessrange.csv"), show_col_types = FALSE)

brand_origin <- readr::read_csv(here::here("inputs/data/clean/brand_origin.csv"), show_col_types = FALSE)
```

# Introduction

@@

The roots of colorism in Japan and India have historical and cultural origins that have contributed to the perpetuation of this issue in modern society. In Japan, the association of fair skin with beauty and status can be traced back to its aristocracy, who were able to avoid outdoor labour and maintain a pale complexion [@japan]. This idea became ingrained in Japanese society and is reinforced through media, advertising, and popular culture. The influence of Western beauty standards, introduced through the influx of mass media from the United States after World War II, has also contributed to the shift towards lighter skin tones in Japan [@japan].

Similarly, in India, the issue of colorism has been exacerbated by the history of colonialism, with the British favouring Indians with lighter skin for government jobs. This discrimination based on skin colour has persisted in Indian society, with fair skin being equated with higher social status and dark skin being associated with lower status [@india]. The impacts of colorism in India are widespread, affecting social mobility, education, employment, and marriage.

In addition to the negative impact on individuals, colorism also has wider societal consequences. Individuals with darker skin tones face exclusion and marginalization, as well as limited access to products and services, leading to unequal opportunities in various aspects of life [@japan]. The globalization of beauty standards has further compounded the issue, with Western ideals of beauty being prioritized and perpetuated by the beauty industry.

To better understand the issue of colorism in Japan and India, the present study draws on data from an article published by The Pudding, a digital publisher specializing in data journalism. The original article examined the lack of diversity in makeup shades offered by major cosmetic brands [@pudding]. However, the current study will focus specifically on the context of Asia and the role of colorism in perpetuating limited shade ranges, with a particular focus on Japan and India.

@@

# Data

This paper was produced using the R statistical programming language [@citeR]. here was used to reference file locations [@here]. The data was examined and cleaned using the packages janitor [@janitor], dplyr [@dplyr], and tidyverse [@tidyverse]. Tables were made knitr [@knitr] and broom [@broom], and formatted with kableExtra [@kableExtra]. ggplot2 [@ggplot2] was used to plot and scale the graphs.

## The Dataset

The dataset was specifically curated for application in The Pudding essay entitled "Beauty Brawl," which was published in June of 2018 [@pudding]. The data was obtained through a systematic process that involved identifying prominent beauty brands in the United States, Nigeria, India, and Japan, as well as consulting various sources that verified their status as best-selling products within their respective domestic markets. The research team accessed each of the brand's official websites in May of 2018 and isolated their liquid foundation collection that possessed the most extensive variety of available shades. For each colour swatch displayed for the product, the corresponding hex colour values were recorded. Subsequently, Adobe Photoshop was utilized to extract the lightness value of each colour using the CIE Lab colour model.

To further classify the sampled products, two additional columns were incorporated into the dataset. These columns included "Brand," which provided the complete written title of the brand responsible for producing the specific foundation shade, and "Product," which listed the full name of the sampled foundation product. It should be noted that for certain brands, this foundation line represented their sole range of liquid foundation, while for others, it constituted the product line containing the largest quantity of available shades.

@@

 * 0: Fenty Beauty's PRO FILT'R Foundation Only
 * 1: Make Up For Ever's Ultra HD Foundation Only
 * 2: US Best Sellers
 * 3: BIPOC-recommended Brands with BIPOC Founders
 * 4: BIPOC-recommended Brands with White Founders
 * 5: Nigerian Best Sellers
 * 6: Japanese Best Sellers
 * 7: Indian Best Sellers

The dataset included information on the hexadecimal colour code (hex), hue (angle on the colour wheel), saturation (degree of colour/chroma), and brightness (also known as value, which measures the lightness or darkness halfway point) values of the foundation shades. The lightness (the relative degree of black or white) values were derived using the CIE Lab colour model, which is predicated on the human perception of colour. The numerical values in the CIE Lab model describe the full spectrum of colours that are visible to individuals with normal vision. As the CIE Lab model represents how a colour appears rather than specifying the quantity of a particular colourant required for a particular device (such as a digital camera, monitor, or desktop printer) to generate colours, it is regarded as a device-independent colour model. To ensure reliable and consistent colour transformation from one colour space to another, colour management systems use the CIE Lab model as a reference point [@adobe].

@@

## Data Cleaning

@@

```{r}
#| messages: false
#| echo: false
#| warning: false

#Create table to summarize lightness range

 summary <- brand_origin |>
  tabyl(group, light_range) |>
  adorn_totals("col")

colnames(summary) <- c("Country", "20 - 30", "50-60", "60-70", "70-80", "80-90", "Total")

summary |>
  kable(caption = "Table 1: Total number of products by lightness range in India & Japan") |>
  kable_styling(full_width = F) |>
  add_header_above(c(" " = 1, "Lightness Range" = 6))

```

@@

```{r}
#| messages: false
#| echo: false
#| warning: false

#plot graph to show shade distribution by lightness

brand_origin |>
  ggplot(aes(x = group, y = L, fill = origin)) +
  geom_boxplot() +
  scale_y_continuous(breaks=seq(0, 100, 5)) +
  theme_minimal() +
  labs(x = "Country",
    y = "Lightness",
    title = "Fig. 1: Shade Distribution by Lightness: Domestic vs. International Brands",
    color = "Country",
    caption = "Data source: The Pudding.")
```

```{r}
#| messages: false
#| echo: false
#| warning: false

#plot graph to show shade distribution by saturation

brand_origin |>
  ggplot(aes(x = group, y = S, fill = origin)) +
  geom_boxplot() +
  scale_y_continuous(breaks=seq(0, 1, 0.05)) +
  theme_minimal() +
  labs(x = "Country",
    y = "Saturation",
    color = "Country",
    title = "Fig. 2: Shade Distribution by Saturation: Domestic vs. International Brands",
    caption = "Data source: The Pudding")

```

@@

# Model
Given the similarity in lightness observed in foundation shades across both countries, it was of interest to investigate if any differences in saturation existed. This investigation was motivated by the fact that the local population in each country has unique undertones. Before conducting the analysis, several tests were conducted to verify that the model assumptions (See Appendix A), including linearity, normality, and homoscedasticity of residuals, were satisfied, thereby ensuring that the model was well-suited for the data at hand.

@@

$$L = \beta_0 + \beta_1S + \epsilon$$

@@

- $L$ represents the dependent variable, which is the overall lightness of the foundation shade
- $S$ represents the independent variable, which is the saturation of the foundation shade
- $\beta_0$ represents the intercept of the regression line, which is the predicted value of $L$ when $S$ is equal to zero
- $\beta_1$ represents the slope of the regression line, which is the change in $L$ for a one-unit increase in $S$
- $\epsilon$ represents the random error term, which accounts for variability in $L$ that is not explained by the relationship with $S$

The aim of linear regression is to estimate the values of $\beta_0$ and $\beta_1$ that minimize the sum of squared errors between the predicted and actual values of lightness ($L$) for the given values of saturation ($S$) in the dataset. By minimizing this sum of squared errors, the linear regression model can produce the best-fit line to describe the linear relationship between the two variables, allowing for the estimation of $L$ values based on known $S$ values.

In this project, the lightness variable ($L$) is measured on a scale of 0 to 100, while the saturation variable ($S$) is measured on a scale of 0 to 1. Therefore, the slope coefficient $\beta_1$ in the linear regression model would represent the change in lightness ($L$) for a one-unit increase in saturation ($S$), where a one-unit increase in $S$ corresponds to an increase of 1/100 in the saturation of the foundation shade. The intercept $\beta_0$ in the model would represent the expected value of $L$ when $S$ is equal to zero, which in this case would correspond to the lightness value for a completely desaturated foundation shade.

@@

# Results

```{r}
#| messages: false
#| echo: false
#| warning: false

# create table to summarize regression findings

model <- lm(L ~ S, data = brand_origin)

summary <- tidy(model)

kbl(summary, caption = "Table 2: Linear Regression Model Summary") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)

```

This study employed a linear regression model to investigate the association between the lightness (L) and saturation (S) of foundation shades offered by popular makeup brands in Japan and India. As presented in Table 2, the model yielded an estimated intercept of 100.31483, indicating that the expected lightness of foundation shades when saturation is zero is 100.31483. The model also revealed a statistically significant negative regression coefficient of -60.59635 for saturation (t = -12.98632, p < .001), indicating a significant negative linear relationship between saturation and lightness of foundation shades.

@@

```{r}
#| messages: false
#| echo: false
#| warning: false

#plot graph to show linear regression

brand_origin |>
  ggplot(mapping = aes(x = S, y = L)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE) +
  scale_y_continuous(breaks=seq(0, 100, 10)) +
  scale_x_continuous(breaks=seq(0, 10, 0.10)) +
  theme_minimal() +
  labs(
    y = "Lightness", 
    x = "Saturation", 
    title = "Linear Regression Plot"
  )

```

@@

# Discussion

@@

## Japanese foundation shades tend to be lighter and ashier on average.
```{r}
#| messages: false
#| echo: false
#| warning: false

# plot graph to show relationship in Japan

brand_origin |>
  filter(group == 'Japan') |>
  ggplot(aes(L, S)) +
  geom_point(size = 0.2) +
  facet_wrap(vars(brand)) +
  scale_x_continuous(breaks=seq(50, 100, 5)) +
  theme_minimal() +
   labs(x = "Lightness",
    y = "Saturation",
    title = "Fig. 4: Relationship between Lightness and Saturation in Shades in Japan",
    caption = "Data source: The Pudding")

```

In Japan, a negative linear relationship between the saturation and lightness of foundation shades is observed, as depicted in Figure 4. The data indicates that as the lightness of foundation shades increases, their saturation decreases, suggesting that lighter foundations tend to appear ashier or cooler-toned than their darker counterparts. According to a study conducted by L’Oréal, East Asian women have a skin tone range of 55-75 in lightness with warmer tones [@loreal]. The brands closest to the regression line seen in Figure 3 with the widest range in lightness and saturation are Addiction, NARS, and Shu Uemera, as demonstrated in Figure 4.

When comparing domestic and international brand offerings, it is noteworthy that Japanese brands, including Addiction, Kate, Shu Uemura, and RMK, offer shades in the 85-90 lightness range, which is significantly lighter than the skin tone range. NARS, originally a foreign brand but now a subsidiary of Shiseido, offers a wider range of shades in both saturation and lightness in contrast with Shiseido. Conversely, although Shu Uemera, a Japanese brand, was acquired by L’Oréal, it still maintains a wide distribution. In contrast, the international luxury brand Dior only offers cool-toned shades within the lighter end of the skin tone range.

The data suggest that foundation offerings in Japan tend to skew toward the fairer end of the skin tone range or significantly lighter. While there are options available for Japanese consumers to find foundation within their skin-tone range, the average foundation shade is lighter and ashier, reflecting a preference for fairer skin, and reinforcing the notion that lighter skin is more desirable. This reinforces the societal pressure to conform to certain beauty standards and can exacerbate colorism by perpetuating the notion that lighter skin is superior to darker skin tones [@japan]. The negative correlation between saturation and lightness observed in the data also implies that consumers with warmer undertones may encounter difficulties in finding foundation shades that strike the appropriate balance between warmth and lightness. Specifically, they may find that foundation shades with warm undertones are excessively dark, while those with cooler undertones are excessively light. This highlights the necessity for makeup brands to provide a diverse range of foundation shades that cater to a variety of undertones and levels of saturation.

@@

## Indian foundation shades are significantly lighter than the natural skin tone.
```{r}
#| messages: false
#| echo: false
#| warning: false

# plot graph to show relationship in India

brand_origin |>
  filter(group == 'India') |>
  ggplot(aes(L, S)) +
  geom_point(size = 0.5) +
  facet_wrap(vars(brand), scales = "free") +
  theme_minimal() +
   labs(x = "Lightness",
    y = "Saturation", 
    title = "Fig. 5: Relationship between Lightness and Saturation in Shades in India",
    caption = "Data source: The Pudding")

```

Figure 5 presents a noteworthy disparity in the distribution of foundation shades across various brands concerning their lightness and saturation attributes. Specifically, it appears that domestic brands in India offer fewer foundation shades compared to international brands like L’Oréal and Maybelline. However, despite Indian skin tones falling within a lightness range of 30-65 and exhibiting warm-toned features, the majority of foundation shades offered by international brands are noticeably situated in the 70-85 lightness range [@loreal]. This observation suggests that international brands tend to prioritize whiteness more than local brands.

Nevertheless, it is important to note that L’Oréal is the only international brand that offers a shade of around 30 with higher saturation. In contrast, the darkest shade provided by a domestic brand is approximately 50, offered by Olivia, which presents all of their products with a warmer tone in contrast to other brands. Furthermore, excluding Lakmé and Olivia, all other domestic brands commence their shade range beyond the maximum limit of the skin tone range. This indicates that Indian consumers tend to purchase foundation shades that are significantly lighter and cooler than their natural skin tone.

@@

## Weaknesses & Next Steps

@@

# Appendix

## Model Testing
```{r}
#| messages: false
#| echo: false
#| warning: false
#linearity assumption
plot(model$fitted.values, model$residuals)

#normality assumption
qqnorm(model$residuals)
qqline(model$residuals)

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Colorism and Cosmetics: Investigating Limited Shade Ranges in the Beauty Industry in Japan and India},
  pdfauthor={Laura Lee-Chu},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Colorism and Cosmetics: Investigating Limited Shade Ranges in the
Beauty Industry in Japan and India\thanks{Code and data supporting this
analysis is available at:}}
\author{Laura Lee-Chu}
\date{April 21, 2023}

\begin{document}
\maketitle
\begin{abstract}
This research paper explores the issue of colorism in the context of the
beauty industry in Japan and India. Drawing on data from an article
published by The Pudding, the paper focuses on the association between
the lightness and saturation of foundation shades provided by leading
makeup brands in India and Japan. The findings reveal a preference for
lighter shades in international brands, whereas domestic brands offer a
broader spectrum of shades with warmer undertones. The study uncovers a
negative correlation between the saturation and lightness of foundation
shades, with Japanese foundation shades being paler and having an ashier
tone, and Indian foundation shades being substantially lighter than the
natural skin tone. The scarcity of foundation shades for individuals
with darker skin tones can lead to their marginalization and exclusion,
perpetuating the issue of colorism in the beauty industry.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, interior hidden, boxrule=0pt, enhanced, frame hidden, breakable, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{3}
\tableofcontents
}
\newpage

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

The roots of colorism in Japan and India have historical and cultural
origins that have contributed to the perpetuation of this issue in
modern society. In Japan, the association of fair skin with beauty and
status can be traced back to its aristocracy, who were able to avoid
outdoor labour and maintain a pale complexion (Phoenix 2014). This idea
became ingrained in Japanese society and is reinforced through media,
advertising, and popular culture. The influence of Western beauty
standards, introduced through the influx of mass media from the United
States after World War II, has also contributed to the shift towards
lighter skin tones in Japan (Phoenix 2014).

Similarly, in India, the issue of colorism has been exacerbated by the
history of colonialism, with the British favouring Indians with lighter
skin for government jobs. This discrimination based on skin colour has
persisted in Indian society, with fair skin being equated with higher
social status and dark skin being associated with lower status
(Jayawardene 2016). The impacts of colorism in India are widespread,
affecting social mobility, education, employment, and marriage.

In addition to the negative impact on individuals, colorism also has
wider societal consequences. Individuals with darker skin tones face
exclusion and marginalization, as well as limited access to products and
services, leading to unequal opportunities in various aspects of life
(Phoenix 2014). The globalization of beauty standards has further
compounded the issue, with Western ideals of beauty being prioritized
and perpetuated by the beauty industry.

To better understand the issue of colorism in Japan and India, the
present study draws on data from an article published by The Pudding, a
digital publisher specializing in data journalism. The original article
examined the lack of diversity in makeup shades offered by major
cosmetic brands (Jason Li 2018). However, the current study will focus
specifically on the context of Asia and the role of colorism in
perpetuating limited shade ranges, with a particular focus on Japan and
India.

@@

\hypertarget{data}{%
\section{Data}\label{data}}

This paper was produced using the R statistical programming language (R
Core Team 2022). here was used to reference file locations (Müller
2020). The data was examined and cleaned using the packages janitor
(Firke 2021), dplyr (Wickham et al. 2023), and tidyverse (Wickham et al.
2019). Tables were made knitr (Xie 2023) and broom (0.7.11 2021), and
formatted with kableExtra (Zhu 2021). ggplot2 (Wickham 2016) was used to
plot and scale the graphs.

\hypertarget{the-dataset}{%
\subsection{The Dataset}\label{the-dataset}}

The dataset was specifically curated for application in The Pudding
essay entitled ``Beauty Brawl,'' which was published in June of 2018
(Jason Li 2018). The data was obtained through a systematic process that
involved identifying prominent beauty brands in the United States,
Nigeria, India, and Japan, as well as consulting various sources that
verified their status as best-selling products within their respective
domestic markets. The research team accessed each of the brand's
official websites in May of 2018 and isolated their liquid foundation
collection that possessed the most extensive variety of available
shades. For each colour swatch displayed for the product, the
corresponding hex colour values were recorded. Subsequently, Adobe
Photoshop was utilized to extract the lightness value of each colour
using the CIE Lab colour model.

To further classify the sampled products, two additional columns were
incorporated into the dataset. These columns included ``Brand,'' which
provided the complete written title of the brand responsible for
producing the specific foundation shade, and ``Product,'' which listed
the full name of the sampled foundation product. It should be noted that
for certain brands, this foundation line represented their sole range of
liquid foundation, while for others, it constituted the product line
containing the largest quantity of available shades.

@@

\begin{itemize}
\tightlist
\item
  0: Fenty Beauty's PRO FILT'R Foundation Only
\item
  1: Make Up For Ever's Ultra HD Foundation Only
\item
  2: US Best Sellers
\item
  3: BIPOC-recommended Brands with BIPOC Founders
\item
  4: BIPOC-recommended Brands with White Founders
\item
  5: Nigerian Best Sellers
\item
  6: Japanese Best Sellers
\item
  7: Indian Best Sellers
\end{itemize}

The dataset included information on the hexadecimal colour code (hex),
hue (angle on the colour wheel), saturation (degree of colour/chroma),
and brightness (also known as value, which measures the lightness or
darkness halfway point) values of the foundation shades. The lightness
(the relative degree of black or white) values were derived using the
CIE Lab colour model, which is predicated on the human perception of
colour. The numerical values in the CIE Lab model describe the full
spectrum of colours that are visible to individuals with normal vision.
As the CIE Lab model represents how a colour appears rather than
specifying the quantity of a particular colourant required for a
particular device (such as a digital camera, monitor, or desktop
printer) to generate colours, it is regarded as a device-independent
colour model. To ensure reliable and consistent colour transformation
from one colour space to another, colour management systems use the CIE
Lab model as a reference point (Adobe 2022).

@@

\hypertarget{data-cleaning}{%
\subsection{Data Cleaning}\label{data-cleaning}}

@@

\begin{table}

\caption{Table 1: Total number of products by lightness range in India & Japan}
\centering
\begin{tabular}[t]{l|r|r|r|r|r|r}
\hline
\multicolumn{1}{c|}{ } & \multicolumn{6}{c}{Lightness Range} \\
\cline{2-7}
Country & 20 - 30 & 50-60 & 60-70 & 70-80 & 80-90 & Total\\
\hline
India & 1 & 3 & 14 & 23 & 16 & 57\\
\hline
Japan & 0 & 3 & 12 & 32 & 27 & 74\\
\hline
\end{tabular}
\end{table}

@@

\includegraphics{paper_files/figure-pdf/unnamed-chunk-3-1.pdf}

\includegraphics{paper_files/figure-pdf/unnamed-chunk-4-1.pdf}

@@

\hypertarget{model}{%
\section{Model}\label{model}}

Given the similarity in lightness observed in foundation shades across
both countries, it was of interest to investigate if any differences in
saturation existed. This investigation was motivated by the fact that
the local population in each country has unique undertones. Before
conducting the analysis, several tests were conducted to verify that the
model assumptions (See Appendix A), including linearity, normality, and
homoscedasticity of residuals, were satisfied, thereby ensuring that the
model was well-suited for the data at hand.

@@

\[L = \beta_0 + \beta_1S + \epsilon\]

@@

\begin{itemize}
\tightlist
\item
  \(L\) represents the dependent variable, which is the overall
  lightness of the foundation shade
\item
  \(S\) represents the independent variable, which is the saturation of
  the foundation shade
\item
  \(\beta_0\) represents the intercept of the regression line, which is
  the predicted value of \(L\) when \(S\) is equal to zero
\item
  \(\beta_1\) represents the slope of the regression line, which is the
  change in \(L\) for a one-unit increase in \(S\)
\item
  \(\epsilon\) represents the random error term, which accounts for
  variability in \(L\) that is not explained by the relationship with
  \(S\)
\end{itemize}

The aim of linear regression is to estimate the values of \(\beta_0\)
and \(\beta_1\) that minimize the sum of squared errors between the
predicted and actual values of lightness (\(L\)) for the given values of
saturation (\(S\)) in the dataset. By minimizing this sum of squared
errors, the linear regression model can produce the best-fit line to
describe the linear relationship between the two variables, allowing for
the estimation of \(L\) values based on known \(S\) values.

In this project, the lightness variable (\(L\)) is measured on a scale
of 0 to 100, while the saturation variable (\(S\)) is measured on a
scale of 0 to 1. Therefore, the slope coefficient \(\beta_1\) in the
linear regression model would represent the change in lightness (\(L\))
for a one-unit increase in saturation (\(S\)), where a one-unit increase
in \(S\) corresponds to an increase of 1/100 in the saturation of the
foundation shade. The intercept \(\beta_0\) in the model would represent
the expected value of \(L\) when \(S\) is equal to zero, which in this
case would correspond to the lightness value for a completely
desaturated foundation shade.

@@

\hypertarget{results}{%
\section{Results}\label{results}}

\begin{table}

\caption{Table 2: Linear Regression Model Summary}
\centering
\begin{tabular}[t]{l|r|r|r|r}
\hline
term & estimate & std.error & statistic & p.value\\
\hline
(Intercept) & 100.31483 & 1.962350 & 51.11973 & 0\\
\hline
S & -60.59635 & 4.666169 & -12.98632 & 0\\
\hline
\end{tabular}
\end{table}

This study employed a linear regression model to investigate the
association between the lightness (L) and saturation (S) of foundation
shades offered by popular makeup brands in Japan and India. As presented
in Table 2, the model yielded an estimated intercept of 100.31483,
indicating that the expected lightness of foundation shades when
saturation is zero is 100.31483. The model also revealed a statistically
significant negative regression coefficient of -60.59635 for saturation
(t = -12.98632, p \textless{} .001), indicating a significant negative
linear relationship between saturation and lightness of foundation
shades.

@@

\includegraphics{paper_files/figure-pdf/unnamed-chunk-6-1.pdf}

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

@@

\hypertarget{japanese-foundation-shades-tend-to-be-lighter-and-ashier-on-average.}{%
\subsection{Japanese foundation shades tend to be lighter and ashier on
average.}\label{japanese-foundation-shades-tend-to-be-lighter-and-ashier-on-average.}}

\includegraphics{paper_files/figure-pdf/unnamed-chunk-7-1.pdf}

In Japan, a negative linear relationship between the saturation and
lightness of foundation shades is observed, as depicted in Figure 4. The
data indicates that as the lightness of foundation shades increases,
their saturation decreases, suggesting that lighter foundations tend to
appear ashier or cooler-toned than their darker counterparts. According
to a study conducted by L'Oréal, East Asian women have a skin tone range
of 55-75 in lightness with warmer tones (Stephanie Nouveau 2014). The
brands closest to the regression line seen in Figure 3 with the widest
range in lightness and saturation are Addiction, NARS, and Shu Uemera,
as demonstrated in Figure 4.

When comparing domestic and international brand offerings, it is
noteworthy that Japanese brands, including Addiction, Kate, Shu Uemura,
and RMK, offer shades in the 85-90 lightness range, which is
significantly lighter than the skin tone range. NARS, originally a
foreign brand but now a subsidiary of Shiseido, offers a wider range of
shades in both saturation and lightness in contrast with Shiseido.
Conversely, although Shu Uemera, a Japanese brand, was acquired by
L'Oréal, it still maintains a wide distribution. In contrast, the
international luxury brand Dior only offers cool-toned shades within the
lighter end of the skin tone range.

The data suggest that foundation offerings in Japan tend to skew toward
the fairer end of the skin tone range or significantly lighter. While
there are options available for Japanese consumers to find foundation
within their skin-tone range, the average foundation shade is lighter
and ashier, reflecting a preference for fairer skin, and reinforcing the
notion that lighter skin is more desirable. This reinforces the societal
pressure to conform to certain beauty standards and can exacerbate
colorism by perpetuating the notion that lighter skin is superior to
darker skin tones (Phoenix 2014). The negative correlation between
saturation and lightness observed in the data also implies that
consumers with warmer undertones may encounter difficulties in finding
foundation shades that strike the appropriate balance between warmth and
lightness. Specifically, they may find that foundation shades with warm
undertones are excessively dark, while those with cooler undertones are
excessively light. This highlights the necessity for makeup brands to
provide a diverse range of foundation shades that cater to a variety of
undertones and levels of saturation.

@@

\hypertarget{indian-foundation-shades-are-significantly-lighter-than-the-natural-skin-tone.}{%
\subsection{Indian foundation shades are significantly lighter than the
natural skin
tone.}\label{indian-foundation-shades-are-significantly-lighter-than-the-natural-skin-tone.}}

\includegraphics{paper_files/figure-pdf/unnamed-chunk-8-1.pdf}

Figure 5 presents a noteworthy disparity in the distribution of
foundation shades across various brands concerning their lightness and
saturation attributes. Specifically, it appears that domestic brands in
India offer fewer foundation shades compared to international brands
like L'Oréal and Maybelline. However, despite Indian skin tones falling
within a lightness range of 30-65 and exhibiting warm-toned features,
the majority of foundation shades offered by international brands are
noticeably situated in the 70-85 lightness range (Stephanie Nouveau
2014). This observation suggests that international brands tend to
prioritize whiteness more than local brands.

Nevertheless, it is important to note that L'Oréal is the only
international brand that offers a shade of around 30 with higher
saturation. In contrast, the darkest shade provided by a domestic brand
is approximately 50, offered by Olivia, which presents all of their
products with a warmer tone in contrast to other brands. Furthermore,
excluding Lakmé and Olivia, all other domestic brands commence their
shade range beyond the maximum limit of the skin tone range. This
indicates that Indian consumers tend to purchase foundation shades that
are significantly lighter and cooler than their natural skin tone.

@@

\hypertarget{weaknesses-next-steps}{%
\subsection{Weaknesses \& Next Steps}\label{weaknesses-next-steps}}

@@

\hypertarget{appendix}{%
\section{Appendix}\label{appendix}}

\hypertarget{model-testing}{%
\subsection{Model Testing}\label{model-testing}}

\includegraphics{paper_files/figure-pdf/unnamed-chunk-9-1.pdf}
